---
title: "SambaR"
output: html_notebook
editor_options: 
  chunk_output_type: inline
---

#Install packages, load libraries
```{r}
#install.packages("adgenet")
library(adegenet)
#install.packages("vcfR")
library(vcfR)
#install.packages("hierfstat")
library(hierfstat)
#install.packages("pegas")
library(pegas)
#install.packages("mmod")
library(mmod)
#if (!requireNamespace("BiocManager", quietly = TRUE))
    #install.packages("BiocManager")

#BiocManager::install("LEA")
library(LEA)
#install.packages("StAMPP")
library(StAMPP)
source("https://github.com/mennodejong1986/SambaR/raw/master/SAMBAR_v1.08.txt")
getpackages()
#install.packages("phangorn")
library(phangorn)
```

####POPS#####
#Input VCF file from STACKS output and change format to GENIND file for adgenet
```{r}
vcf <- read.vcfR("populations.snps.vcf");
dat1 <- vcfR2genind(vcf);
vcf2lfmm("populations.snps.vcf")
head(vcf)
```
#Create population list for GENIND file that corresponds to individuals, add poplist to data objects
```{r}
poplist <-
  c('AC','AC','AC','AC','AC','AC','AC','AC','AC','AC','CA','CA','CA','CA','CA','CA','CA','CA','CA','CA','CH','PO','PO','PO','PO','PO','PO','PO','PO','PO','PO','RP','RP','RP','RP','RP','RP','RP','RP','RP','RP','SA','SA','SA','SA','SA','SA','SA','SA','SA','SA','SR','SR','SR','SR','SR','SR','SR','SR','SR','SR')

pop(dat1)<-as.factor(poplist)

dat2 <- genind2hierfstat(dat1)
```
#Create dat3 genlight object to be used in sambaR, add poplist to data
```{r}
dat3 <- vcfR2genlight(vcf)
pop(dat3)<-as.factor(poplist)
```
#Run sambaR with dat3, calculate population genetic statistics
```{r}
genlight2sambar("dat3",do_confirm=TRUE,allow_edit=TRUE)
filterdata(indmiss=1.0,snpmiss=0.1,min_mac=2,dohefilter=TRUE,min_spacing=500,nchroms=12,TsTvfilter=NULL)
calcdistance(dodistgenpop=FALSE)
calcdiversity()
```

#####MORPHS#####
#Input VCF file from STACKS output and change format to GENIND file for adgenet
```{r}
vcf_morphs <- read.vcfR("morphs/input_files/populations.snps.vcf");
dat1_morphs <- vcfR2genind(vcf);
vcf2lfmm("morphs/input_files/populations.snps.vcf")
head(vcf_morphs)
```
#Create population list for GENIND file that corresponds to individuals, add poplist to data objects
```{r}
poplist_morphs <-
  c('striped','striped','striped','striped','striped','striped','striped','striped','striped','striped','hybrid','hybrid','hybrid','hybrid','hybrid','hybrid','hybrid','hybrid','hybrid','hybrid','hybrid','striped','striped','striped','striped','striped','striped','striped','striped','striped','striped','hybrid','hybrid','hybrid','hybrid','hybrid','hybrid','hybrid','hybrid','hybrid','hybrid','banded','banded','banded','banded','banded','banded','banded','banded','banded','banded','banded','banded','banded','banded','banded','banded','banded','banded','banded','banded')

pop(dat1_morphs)<-as.factor(poplist_morphs)

dat2_morphs <- genind2hierfstat(dat1_morphs)
```
#Create dat3 genlight object to be used in sambaR, add poplist to data
```{r}
dat3_morphs <- vcfR2genlight(vcf_morphs)
pop(dat3_morphs)<-as.factor(poplist_morphs)
```
#Run sambaR with dat3, calculate population genetic statistics
```{r}
genlight2sambar("dat3_morphs",do_confirm=TRUE,allow_edit=TRUE)
filterdata(indmiss=1.0,snpmiss=0.1,min_mac=2,dohefilter=TRUE,min_spacing=500,nchroms=12,TsTvfilter=NULL)
calcdistance(dodistgenpop=FALSE)
calcdiversity()
```